Long range correlations and their event scale dependence in high multiplicity pp collisions at $\sqrt{s} = 13$~TeV

### 2020-05-28 paper.tex
abstract improved

To further investigate the ridge effect in small systems, we present the new results of long-range correlations as a function of transverse momentum of jets in very high-multiplicity pp collisions at center-of-mass energy $\sqrt{s} = 13$~TeV with ALICE. The study benefit from a dedicated high-multiplicity trigger implemented in ALICE since 2016. Jet events are selected by two methods. The first one is done by seeing the transverse momentum of  leading particle in the pseudorapidity range $|\eta|<0.9$. The second method is done by reconstruction of charged jets using the anti-$k_\mathrm{T}$ algorithm with resolution parameter $R=0.4$ in $|\eta_\mathrm{jet}|<0.4$. The measured ridge yield is consistent with the previous results from other LHC experiments. Furthermore, the ridge yield is found to be independent of the energy scale of the hard scattering process. This observation can help identify the origins of the ridge in small systems.

>>>>

To further investigate the ridge effect in small systems, we present new results of long-range correlations as a function of transverse momentum of jets in very high-multiplicity pp collisions at center-of-mass energy $\sqrt{s} = 13$~TeV with ALICE. The ridge yield is investigated in the pseudorapidity difference range $1.6<|\Delta \eta|<1.8$ of two-particle correlations. Jet events are selected by two methods. The first one is done by seeing the transverse momentum of  leading particle in the pseudorapidity range $|\eta|<0.9$.  The second method is done by reconstruction of charged jets using the anti-$k_\mathrm{T}$ algorithm with resolution parameter $R=0.4$ in the pseudorapidity range of jets $|\eta_\mathrm{jet}|<0.4$. The study benefit from a dedicated high-multiplicity trigger implemented in ALICE since 2016. The measured ridge yield is consistent with the previous results from other LHC experiments. Furthermore, the ridge yield is found to be independent of the energy scale of the hard scattering process. This observation can help identify the origins of the ridge in small systems.
